Exposure Consequences - Statistics and Figures

### 2018-07-25 ManuscriptMaterials.Rmd
update URLs of data on OSF

```{r eval=F}
participants <- load.DownloadDataframe(informationURLs['demographics'],'participants_exposure.csv')
participants <- participants[which(participants$participant %in% OKparticipants),]
```

@@

```{r eval=F}
c('mean'=mean(participants$age), 'sd'=sd(participants$age))
```

@@

```{r eval=F}
table(participants$sex)
```

>>>>

```{r}
participants <- load.DownloadDataframe(informationURLs['demographics'],'participants_exposure.csv')
if (selectPerformance) {
  participants <- participants[which(participants$participant %in% OKparticipants),]
}
```

@@

```{r}
c('mean'=mean(participants$age), 'sd'=sd(participants$age))
```

@@

```{r}
table(participants$sex)
```
